Sketch Recognition using Enhanced Particle Swarm Optimization

### 2010-11-25 trunk/Swarm/swarmModified.tex
edit to sut the format for FCI

\documentclass[12pt,1p,times]{elsarticle}%[10pt]{article}
%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%\usepackage{spconf}
\usepackage{amsmath}
\usepackage[dvips,pdftex]{graphicx}
%\usepackage{named}
\usepackage{hyperref}
%\usepackage[dvips,pdftex]{hyperref}
\usepackage{subfigure}
\usepackage{array}
\usepackage{amssymb}
%\usepackage{epsfig}
%\usepackage{epstopdf}

@@

% \biboptions{}
\begin{document}

\begin{frontmatter}
%% Title, authors and addresses

@@

\author[Eri]{Maha El Meseery \corref{cor1} }%,
\ead{melmeseery@eri.sci.eg}
\author[Eri]{Mahmoud Fakhr El Din}
\ead{ mafakhr@mcit.gov.eg}
\author[metro]{Tarek abouldahab}
\ead{heshoaboda@hotmail.com}

\address[Eri]{Signals Processing Group, Computers and Systems Department,
  Electronic Research Institute,Cairo, Egypt.}
  \address[metro]{Cairo Metro Company, Ministry of transport ,Cairo, Egypt.}
\cortext[cor1]{ Corresponding author}

% \twoauthors
% {\sthanks{Corresponding Author},}
% 	{Signals Processing Group \\ Computers and Systems Department \\
%   Electronic Research Institute\\Cairo, Egypt\\
% 	melmeseery@eri.sci.eg, mafakhr@mcit.gov.eg}
%   {} {Cairo Metro Company \\
%   Ministry of transport \\Cairo, Egypt\\ heshoaboda@hotmail.com}

%\maketitle
 \begin{abstract}
%This study

Sketches and drawings are widely used as a simple method of expressing thought and designs. The goal of this paper is to improve our sketch recognition system by using an enhanced particle swarm optimization algorithm. The Enhanced Particle Swarm Optimization (EPSO) is based on the perturbation of the particle velocity is used to optimally segment the strokes the user draws into meaningful geometric primitives.  These geometric primitives are grouped to formulate symbols which are further identified using a Support Vector Machines (SVM) classifier. Experiments were conducted on the benchmark dataset of simple presentation (Hs-DS) symbols. Results show that that the enhanced particle swarm optimization improves the final recognition accuracy.

@@

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% MSC codes here, in the form: \MSC code \sep code
Sketch Recognition, Particle Swarm Optimization
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}
\end{frontmatter}

%\pagenumbering{arabic}
 \section{Introduction}

@@

\bibliographystyle{elsarticle-num-names}
\bibliography{../../../neededfiles/Bibliographies/Mybibliography}

>>>>

%\documentclass[a4paper, twoside]{article}

%%\usepackage{icgst}
\documentclass[12pt,times,a4paper]{article}%[10pt]{article}
%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%\usepackage{spconf}
\usepackage{amsmath}
%\usepackage{named}
%\usepackage{hyperref}
%\usepackage[dvips,pdftex]{hyperref}
%\usepackage{subfigure}
\usepackage{array}
\usepackage{amssymb}
%\usepackage{epsfig}
%\usepackage{epstopdf}
%\usepackage{xltxtra}
\usepackage{graphicx}
\usepackage{sectsty}
\sectionfont{\normalsize  }
\subsectionfont{ \normalsize\it \textbf }
\subsubsectionfont{\normalsize \it \textbf }
%\paragraphfont{\large\it}
%\subparagraphfont{\normalsize\it}

@@

% \biboptions{}
\setlength\hoffset{0in}
% \setlength\topmargin{0in}
% \setlength\headheight{0in}
% \setlength\headsep{-0.5in}
% \setlength\textheight{10.0in}
 \setlength\textwidth{7in}
 \setlength\oddsidemargin{-0.5in}
 \setlength\evensidemargin{-0.5in}
% \setlength\parindent{0.25in}
% \setlength\parskip{0.25in} 
\linespread{1.5}

\begin{document}

%\begin{frontmatter}
%% Title, authors and addresses

@@

% \twocolumn[
% \scalebox{1.00}{\includegraphics[width=1.00\textwidth]{aimlhead}}
% \title{Sketch Recognition using Enhanced Particle Swarm Optimization}
% \vspace{0.1in}
% \author{}  
% \begin{center}
% Maha El Meseery\footnote{Corresponding Author }, Mahmoud Fakhr El Din, Tarek abouldahab\\
% \textit{Electronic Research Institute,} Cairo, Egypt,\\
% \textit{ Cairo Metro Company, Ministry of transport }Cairo, Egypt\\
% {melmeseery@eri.sci.eg, mafakhr@mcit.gov.eg,  heshoaboda@hotmail.com},\\
% %\texttt{http://www.faculty.university.edu.any}
% \end{center}
% \vspace{0.25in} 
% ]

% \twoauthors
% 
%  {Maha El Meseery, Mahmoud Fakhr El Din}
% 	{Signals Processing Group \\ Computers and Systems Department \\
%   Electronic Research Institute\\Cairo, Egypt\\
% 	melmeseery@eri.sci.eg, mafakhr@mcit.gov.eg} 
% 	 {Tarek abouldahab\sthanks{Corresponding Author}} {Cairo Metro Company \\
%   Ministry of transport \\Cairo, Egypt\\ heshoaboda@hotmail.com}

% \author[Eri]{Maha El Meseery \corref{cor1} }%,
% \ead{melmeseery@eri.sci.eg}
% \author[Eri]{Mahmoud Fakhr El Din}
% \ead{ mafakhr@mcit.gov.eg}
% \author[metro]{Tarek abouldahab}
% \ead{heshoaboda@hotmail.com}
% 
% \address[Eri]{Signals Processing Group, Computers and Systems Department,
%   Electronic Research Institute,Cairo, Egypt.}
%   \address[metro]{Cairo Metro Company, Ministry of transport ,Cairo, Egypt.}
% \cortext[cor1]{ Corresponding author}

\author{
\small{
Maha El Meseery \footnote{Corresponding Author} \textsuperscript{a}, Mahmoud Fakhr El Din \textsuperscript{a}, Tarek abouldahab \textsuperscript{b}}\\
 \textsuperscript{a} \small{Signals Processing Group, Computers and Systems Department,}\\ \small{ Electronic Research Institute, Cairo, Egypt.}\\
  \small {\textsuperscript{b}Cairo Metro Company ,
   Ministry of transport , Cairo, Egypt.}\\
   \small{melemseery@eri.sci.eg,  mafakhr@mcit.gov.eg, heshoaboda@hotmail.com
   }
}
\date{}
% {\sthanks{Corresponding Author},}
% 	{Signals Processing Group \\ Computers and Systems Department \\
%   Electronic Research Institute\\Cairo, Egypt\\
% 	melmeseery@eri.sci.eg, mafakhr@mcit.gov.eg}
%   {Tarek abouldahab} {Cairo Metro Company \\
%   Ministry of transport \\Cairo, Egypt\\ heshoaboda@hotmail.com}
%  {Maha El Meseery \sthanks{Corresponding Author}, Mahmoud Fakhr El Din}
% 	{Signals Processing Group \\ Computers and Systems Department \\
%   Electronic Research Institute\\Cairo, Egypt\\
% 	melmeseery@eri.sci.eg, mafakhr@mcit.gov.eg}
% 	 {Tarek abouldahab\sthanks{Corresponding Author}} {Cairo Metro Company \\
%   Ministry of transport \\Cairo, Egypt\\ heshoaboda@hotmail.com}

\maketitle
 \begin{abstract}

%This study 
Sketches and drawings are widely used as a simple method of expressing thought and designs. The goal of this paper is to improve our sketch recognition system by using an enhanced particle swarm optimization algorithm. The Enhanced Particle Swarm Optimization (EPSO) is based on the perturbation of the particle velocity is used to optimally segment the strokes the user draws into meaningful geometric primitives. These geometric primitives are grouped to formulate symbols which are further identified using a Support Vector Machines (SVM) classifier. Experiments were conducted on the benchmark dataset of simple presentation (Hs-DS) symbols. Results show that the enhanced particle swarm optimization improves the final recognition accuracy.

@@

% \begin{keyword}
% %% keywords here, in the form: keyword \sep keyword
% 
% %% MSC codes here, in the form: \MSC code \sep code
% Sketch Recognition, Particle Swarm Optimization
% %% or \MSC[2008] code \sep code (2000 is the default)
% 
% \end{keyword}
%\end{frontmatter}
\textit{\textbf{Keywords:} Sketch Recognition, Particle Swarm Optimization.}
%\pagenumbering{arabic}
 \section{Introduction}

@@

%\bibliographystyle{natbib}
\bibliographystyle{ieeetr}
\bibliography{../../../neededfiles/Bibliographies/Mybibliography}
